\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-11-10 manuscript.Rnw
Replace 3-step process figure with LaTeX tikz figure

%% other packages
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{caption} 
\captionsetup[table]{skip=5pt}

@@

The analysis is performed in the next three steps as shown in Figure~\ref{fig:econ-eval-process-hesim}. First, the disease progression, costs, and utility submodels are parameterized using ``estimation'' datasets. Next, the submodels are combined to construct an economic model. The economic model is then used to simulate, disease progression, QALYs, and costs as a function of ``input data''. The input data always contains variables describing the target population and treatment strategies of interest, but can also contain variables related to time to facilitate use of time-varying covariates or parameters. Finally, the simulated outcomes are used to perform decision analysis, currently limited to CEA. All models are simulated using PSA so that decision uncertainty can be represented.

\begin{figure}[h]
\centering
\includegraphics[width = 15cm]{econ-eval-process-hesim.png}
\caption{Economic modeling process}\label{fig:econ-eval-process-hesim}
\end{figure}

The three economic models described in Section~\ref{sec:model-taxonomy} are implemented as the \pkg{R6} classes \code{CohortDtstm}, \code{IndivCtstm}, and \code{Psm}. Each class contains methods for simulating disease progression, QALYs, and costs These methods are made possible by separate \pkg{R6} classes for the disease, utility, and cost submodels.

>>>>

%% other packages
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{caption} 
\captionsetup[table]{skip=5pt}

@@

The analysis is performed in the next three steps as shown in Figure~\ref{fig:econ-eval-process-hesim}. First, the disease progression, costs, and utility submodels are parameterized using ``estimation'' datasets. Next, the submodels are combined to construct an economic model. The economic model is then used to simulate, disease progression, QALYs, and costs as a function of ``input data''. The input data always contains variables describing the target population and treatment strategies of interest, but can also contain variables related to time to facilitate use of time-varying covariates or parameters. Finally, the simulated outcomes are used to perform decision analysis within a cost-effectiveness framework. While other approaches such as multi-criteria decision analysis (MCDA) could, in principle, be used as well, only CEA is currently supported. All models are simulated using PSA so that decision uncertainty can be represented.

\begin{figure}[h]
\centering
\begin{tikzpicture}
% Parameterization
\node[draw, minimum height=4cm, minimum width=3.5cm, font=\footnotesize, text depth = 3.5cm] (A) at (-5,0) {\textbf{1. Parameterization}};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (-5, .8){Disease model};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (-5, -.2){Utility model};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (-5, -1.2){Cost model(s)};

% Simulation
\node[draw, minimum height=4cm, minimum width=3.5cm, font=\footnotesize, text depth = 3.5cm] (B) at (0,0) {\textbf{2. Simulation}};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (0, .8){Disease model};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (0, -.2){Utility model};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (0, -1.2){Cost model(s)};

% Decision analysis
\node[draw, minimum height=4cm, minimum width=3.5cm, font=\footnotesize, text depth = 3.5cm] (C) at (5,0) {\textbf{3. Decision analysis}};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (5, .3){CEA};
\node[draw,fill=white, minimum height=.8cm, minimum width=2.5cm, font=\footnotesize] at (5, -.7){MCDA};

% Data
\node[draw, above = .5 of A, minimum width=3cm, font=\footnotesize] (D) {Estimation data};
\node[draw, above = .5 of B, minimum width=3cm, font=\footnotesize] (E) {Input data};

% Arrows
\draw [thick, ->] (A.east) -- (B.west);
\draw [thick, ->] (B.east) -- (C.west);
\draw [thick, ->] (D.south) -- (A.north);
\draw [thick, ->] (E.south) -- (B.north);

\end{tikzpicture}
\caption{Economic modeling process}\label{fig:econ-eval-process-hesim}
\end{figure}

The three economic models described in Section~\ref{sec:model-taxonomy} are implemented as the \pkg{R6} classes \code{CohortDtstm}, \code{IndivCtstm}, and \code{Psm}. Each class contains methods for simulating disease progression, QALYs, and costs. These methods are made possible by separate \pkg{R6} classes for the disease, utility, and cost submodels. The remainder of this section describes the framework for parameterization and simulation. The cost-effectiveness framework is described in Section~\ref{sec:cea}.
